Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de~Rham complex over convex domains and domains with shellable triangulations

### 2025-01-17 main.tex
table for PF constants with mixed boundary conditions

We first assess the constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
which relies on estimates for the Bogovski\u{\i} operator over an auxiliary reference domain.
We compare computed Poincar\'e--Friedrichs constants over the reference tetrahedron with tangential boundary conditions along a few faces. 
% We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex. Numerical examples indicate that this holds for $p=2$.

\begin{table}[t]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
                           & $\grad$           & $\curl$           & $\divergence$   \\ \hline
        $l=0$              & 0.08625017654     & 0.1453729386      & 0.2601720480    \\ \hline
        $l=1$              & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
        $l=2$              & 0.1450219664      & 0.2428248005      & 0.1845090722    \\ \hline
        $l=3$              & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
        $\Gamma=\emptyset$ & 0.2631059409      & 0.1458215887      & 0.08740665548   \\ \hline
    \end{tabular}
    \caption{
    Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
    where boundary conditions are imposed along the faces $F_{\ell}, \dots, F_3$, or no boundary conditions are imposed (last row). 
    Computed via lowest-order finite element methods. The upper bound in Lemma~\ref{} is $0.45015815807$.
    }\label{table:referencepoincarefriedrichs}
\end{table}

>>>>

We first assess the Poincar\'e--Friedrichs constant in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative},
where tangential boundary conditions hold along a few faces. 
We tabulate reference Poincar\'e--Friedrichs constants over the reference tetrahedron in Table~\ref{table:referencepoincarefriedrichs},
which are computed via a higher-order finite element method over a mesh after three iterations of uniform refinement.

The aforementioned lemma gives an upper bound of $\sqrt{2}/\pi \approx 0.45015815807$,
which is an overestimate of at most a factor of six.
We take this as an indication that the estimate is within feasible range. 
We expect the bound to deteriorate as the eccentricity of the tetrahedron increases.

% We conjecture that over convex domains $\Omega$, the Poincar\'e--Friedrichs constant of the gradient $\grad : W^{1,p}(\Omega) \rightarrow \bfL^{p}(\Omega)$ is an upper estimate for other Poincar\'e--Friedrichs constants in de~Rham complex. Numerical examples indicate that this holds for $p=2$.

\begin{table}[t]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
                           & $\grad$           & $\curl$           & $\divergence$   \\ \hline
        $l=0$              & 0.08625017654     & 0.1453729386      & 0.2601720480    \\ \hline
        $l=1$              & 0.1093817645      & 0.1829680131      & 0.3493931507    \\ \hline
        $l=2$              & 0.1450219664      & 0.2428248005      & 0.1845090722    \\ \hline
        $l=3$              & 0.2057601732      & 0.1527746636      & 0.1223402289    \\ \hline
        $\Gamma=\emptyset$ & 0.2631059409      & 0.1458215887      & 0.08740665548   \\ \hline
    \end{tabular}
    \caption{
    Reference $L^2$ Poincar\'e--Friedrichs constants for the gradient, curl, and divergence operators over the reference tetrahedron,
    where boundary conditions are imposed along the faces $F_{\ell}, \dots, F_3$, or no boundary conditions are imposed (last row). 
    Computed via lowest-order finite element methods. The upper bound in Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} is $0.45015815807$.
    }\label{table:referencepoincarefriedrichs}
\end{table}
